Climate control for performant HPUs

### 2014-04-09 docs/draft/draft1.tex
update to manuscript -- added test and priming images

>>>>

We paid 900 AMT workers to perform an image-labelling task.  A task consisted 
of labelling 10 images, with 5 labels each.  The first 5 images were varied 
depending on the priming treatment, while the last 5 images were the same 
accross all treatments.  Ordering of the images was kept constant.

Workers were randomly assigned to one of 6 treatments.  The treatments differed
from one another along two dimensions. The first dimension consisted of 
varying the first 5 images shown to the worker.  This was used to test the
effects of \textit{in-task} priming.

The second dimension concerned disclosure of a (fictitious) organization,
purportedly funding work as part of a research study.  Depending on the 
treatment, one of two funding agencies was presented, or no indication was 
made.

The 5 test images, were chosen carefully with two ideals in mind.  
First, we chose images that we judged would generate a diverse vocabulary of 
labels, such that the effects of priming could be detected.  In other words,
sparse images with a single object in the foreground were not considered good 
candidates, since they would be less likely to elicit labels that varied from 
one worker and one priming treatment to the next.

Second, we chose images which would produce labels belonging to two broad
concepts, which would serve as the targets of our priming: food and culture.  
This created the opportunity to attempt to prime workers in a way that would
bias them toward emitting food-related or culture-related labels.

Under these considerations, we chose the images shown in 
Fig.~\ref{fig:testImages}

\begin{figure*}
	\includegraphics[scale=1.00]{../figs/testImages.png}
	\label{fig:testImages}
\end{figure*}

\begin{figure*}
	\includegraphics[scale=1.00]{../figs/ambiguous.png}
	\label{fig:ambiguous}
\end{figure*}

\begin{figure*}
	\includegraphics[scale=1.00]{../figs/cultural.png}
	\label{fig:cultural}
\end{figure*}

\begin{figure*}
	\includegraphics[scale=1.00]{../figs/ingredients.png}
	\label{fig:ingredients}
\end{figure*}

We chose the three sets of priming images to that end.  The first set, was 
chosen to be 
for the treatment

\textit{culture}, and \textit{food}.
\section*{Results}
\begin{figure*}
	\includegraphics[scale=0.65]{../figs/specificity.pdf}
\end{figure*}
